Bayesian statistics and swine flu

### 2009-09-24 docs/pandemic/bayesPandemic.rnw
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@411 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\begin{frame}[fragile]
\frametitle{Results}
<<mcmcResults,echo=true,fig=false>>=
scale = mcmcScale(params, 0.075,minScale = 0.05 )
paramSample = mcmcPandemic(data,params,priors,sigma=scale,runs=60)
paramSample = paramSample[seq(100,dim(paramSample)[1], by=5),]
dim(paramSample)
colnames(paramSample)
@
\end{frame}

>>>>

\begin{frame}[fragile]
\frametitle{Results}
<<mcmcResults,echo=true,fig=false>>=
scale = mcmcScale(params, 0.075,minScale = 0.05 )
paramSample = mcmcPandemic(data,params,priors,sigma=scale,runs=60, thin = 5)

dim(paramSample)
colnames(paramSample)
@
\end{frame}
